Scale Space Edge Detection

### 2018-03-06 paper.tex
yes
Jon fix this styling when you wake up

%&pdflatex
\documentclass{article}
\usepackage[final]{nips_2017}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{morefloats}
\usepackage{float}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}

@@

\begin{equation}
  G(\Gamma) = \int_{(x;t) \in \Gamma} \sqrt{(G_{\gamma}L)(x;t)} \,\, ds
\end{equation}

where $ds^2=dx^2+dy^2$.

@@

# Define derivative convolution matrices
Dy = Array(parent(Kernel.ando5()[1]))
Dx = Array(parent(Kernel.ando5()[2]))
\end{lstlisting}

@@

\begin{equation}
  \begin{aligned}
    [D_y] &=
    \begin{bmatrix}
      -0.003776 &-0.010199  &0.0  &0.010199  &0.003776 \\
      -0.026786 &-0.070844  &0.0  &0.070844  &0.026786 \\
      -0.046548 &-0.122572  &0.0  &0.122572  &0.046548 \\
      -0.026786 &-0.070844  &0.0  &0.070844  &0.026786 \\
      -0.003776 &-0.010199  &0.0  &0.010199  &0.003776
    \end{bmatrix} \\
    [D_y] &= [D_x]^T
  \end{aligned}
\end{equation}
\section*{References}

>>>>

%&pdflatex
\documentclass{article}
\usepackage[final]{nips_2017}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{morefloats}
\usepackage{float}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{commath}
\usepackage{graphicx}

@@

\begin{equation}
  G(\Gamma) = \int_{(x;t) \in \Gamma} \sqrt{(G_{\gamma}L)(x;t)} \,\, \dif s
\end{equation}

where $\dif s^2=\dif x^2+\dif y^2$.

@@

# Define derivative convolution matrices
Dy = Array(parent(Kernel.ando5()[1]))
Dx = Array(parent(Kernel.ando5()[2]))

# Normalized the derivatives
Dx /= sum(Dx .* (Dx .> 0))
Dy /= sum(Dy .* (Dy .> 0))
\end{lstlisting}

@@

\begin{equation}
  \begin{aligned}
    [D_y] &=
    \begin{bmatrix}
      -0.003776 &-0.010199  &0.0  &0.010199  &0.003776 \\
      -0.026786 &-0.070844  &0.0  &0.070844  &0.026786 \\
      -0.046548 &-0.122572  &0.0  &0.122572  &0.046548 \\
      -0.026786 &-0.070844  &0.0  &0.070844  &0.026786 \\
      -0.003776 &-0.010199  &0.0  &0.010199  &0.003776
    \end{bmatrix} \\
    [D_x] &= [D_y]^T
  \end{aligned}
\end{equation}

From this point, we then can compute the scale space representation of our image and compute its spatial derivatives
The following section of code defines just how to do that.

\begin{lstlisting}
# Scale space representation
L = cat(3, (convolve_gaussian(img, sigma) for sigma in scales)...)

# First order derivatives
Lx = convolve_scale_space(L, Dx)
Ly = convolve_scale_space(L, Dy)

# Second order derivatives
Lxx = convolve_scale_space(Lx, Dx)
Lxy = convolve_scale_space(Lx, Dy)
Lyy = convolve_scale_space(Ly, Dy)

# Third order derivatives
Lxxx = convolve_scale_space(Lxx, Dx)
Lxxy = convolve_scale_space(Lxx, Dy)
Lxyy = convolve_scale_space(Lxy, Dy)
Lyyy = convolve_scale_space(Lyy, Dy)
\end{lstlisting}

By convolving our ando5 derivative matrix with the scale space representation, we can take spatial derivatives in both the $x$ and $y$ dimension. To give an idea of what the images look like, we have the following spatial derivatives of the image below.

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.5]{Images/lx.png}
  \caption{Derivative of image in $x$ direction}
  \label{lx}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[scale=0.5]{Images/ly.png}
  \caption{Derivative of image in $y$ direction}
  \label{ly}
\end{figure}

Now that we have computed the spatial derivatives of the scale space representation of the image, we can check if we fulfill the conditions in (\ref{eq:c1}). 
The next step is to then calculate the edge strength derivatives neccessary to fulfill the conditions of (\ref{eq:c2}).
The code block below shows the computations for the edge strength based on the gradient magnitued and its derivatives.

\newpage

\begin{lstlisting}
# Shape the scales vector to be a vector with depth
scales3 = reshape(scales, 1, 1, length(scales))

# Definition of the gradient edge strength (magnitude)
const GL = scales3.^(gamma).*(Lx.^2+Ly.^2)

# Derivative of edge strength gradinet with respect to scale
const GLt = @. gamma*scales3^(gamma-1)*(Lx^2 + Ly^2) + scales3^gamma*(Lx*(Lxxx + Lxyy) + Ly*(Lxxy + Lyyy))

# Second derivative of edge strength gradinet with respect to scale
const GLtt = @. (gamma*(gamma - 1)*scales3^(gamma - 2)*(Lx^2 + Ly^2) + 2gamma*scales3^(gamma-1)*(Lx*(Lxxx + Lxyy) + Ly*(Lxxy + Lyyy)) + scales3^gamma/2*((Lxxx + Lxyy)^2 + (Lxxy + Lyyy)^2 + Lx*(Lxxxxx + 2Lxxxyy + Lxyyyy) + Ly*(Lxxxxy + 2Lxxyyy + Lyyyyy))) < 0
\end{lstlisting}

\section*{Appendix}

\lstinputlisting[caption={edge\_detect.jl},label=edge_detect]{edge_detect.jl}

\section*{References}
